Sulfur Dioxide on Water's Surface

### 2011-02-24 TransitOrientation.tex
added bit about the normalization for 2d histogrms... about to start more on the transit orientation of the so2
rewrote the so2 transit orientation section with the new images

	The orientation of a \suldiox~molecule during adsorption to, and absorbtion in an aqueous surface was determined through an analysis of the transit SMD simulations. The angles $\theta$ and $\phi$ (figure \ref{fig:water-angles}) were calculated for each timestep of the SMD simulations as the transiting \suldiox~was pulled into the water slab from the gas phase, both in the neat-water and saturated slab systems. The angle cosine values were collected for the 50 simulations of both systems for each distance from the water surface, resulting in the 2-dimensional histograms shown in figure \ref{fig:so2-transit-angles}. Only the surface into which the transiting \suldiox~was steered into is shown for the saturated system's analysis.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/transit-so2-angles/so2-angles-transit.png}
		\caption{\suldiox~molecular orientation distributions during SMD transit simulations into an aqueous slab. Both the neat-water (top row) and saturated (bottom row) data sets were analyzed to determine the angles $\theta$ (left column), and $\phi$ (right column) of the transiting \suldiox. The distributions show angle cosines plotted against the distance of the \suldiox~to the location of the water surface. The data sets were averaged at each distance for the respective 50 simulations.}
		\label{fig:so2-transit-angles}
	\end{center}
\end{figure}

	From its starting position 20\angs above the water surface, until the \suldiox~moves to within 10\angs of the surface of both systems, the orientation is isotropic in $\phi$. The trend for the bisector angle, $\theta$, upon approaching the surface is to become more perpendicular to the surface with the \suldiox~sulfur pointing into the water phase. At the point when the \suldiox~reaches the surface location (distance$=0$), the bisector is mostly perpendicular in both the neat-water and saturated systems. In the distribution of $\phi$, both systems show isotropy in the orientation

  Upon approaching the saturated surface at approx. 5\angs, the \suldiox~$\phi$ orientation distribution begins to cluster near $\cos(\phi)=1$, with the $\theta$ distribution remaining more isotropic, but with a trend of $\cos(\theta)>0$. At 5\angs the \suldiox~begins interacting with the other \suldiox~molecules that sit atop the water, and the resulting orientation distribution suggests that contact with the \suldiox~layer causes the adsorbing molecule to lie more flat to the surface. Within this same region from 0-5\angs above the surface, the $\phi$ distribution of the neat-\wat~system remains isotropic. The intensity of the distribution (darker blue) also indicates that the \suldiox~spends little time in this region, as it is quickly adsorbed further into the water bulk.

>>>>

	The orientation of a \suldiox~molecule throughout the aqueous adsorption process was monitored during the transit SMD simulations. The angles $\theta$ and $\phi$ (figure \ref{fig:water-angles}) were calculated for each timestep of the SMD simulations as the transiting \suldiox~was pulled into the water slab from the gas phase, both in the neat-water and saturated slab systems. The angle cosine values were collected for the 50 simulations of both systems for each distance from the water surface, resulting in the 2-dimensional histograms shown in figure \ref{fig:so2-transit-angles}. Only the surface into which the transiting \suldiox~was steered into is shown for the saturated system's analysis. In all the data sets, the populations of the angle histograms at each distance from the surface were normalized to aid in comparison of regions with differing \suldiox~residence times.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/transit-so2-angles/so2-angles-transit.png}
		\caption{\suldiox~molecular orientation distributions during SMD transit simulations into an aqueous slab. Both the neat-water (top row) and saturated (bottom row) data sets were analyzed to determine the angles $\theta$ (left column), and $\phi$ (right column) of the transiting \suldiox. The distributions show angle cosines plotted against the distance of the \suldiox~to the location of the water surface. The data sets were averaged at each distance for the respective 50 simulations, and every distribution at each distance was normalized such that each histogram has a max population of 1 for purposes of comparison.}
		\label{fig:so2-transit-angles}
	\end{center}
\end{figure}

	From its starting position 20\angs above the water surface, until the \suldiox~moves to within 10\angs of the surface of both systems, the orientation is isotropic in $\theta$ and $\phi$. The bisector angle $\theta$, near to the surface becomes more perpendicular ($\cos(\theta)\approx1$) with the \suldiox~sulfur pointing into the water phase. At the point when the \suldiox~reaches the surface location (distance$=0$), the bisector is perpendicular in both the neat-water and saturated systems. There are differences between the neat-water and saturated systems, however, in the onset points of the orientational preferences.

  % talk about theta differences
  The $\theta$ distribution clearly shows that the \suldiox~is isotropically oriented in the gas-phase and then orients with its bisector perpendicular to the water surface within a certain distance above the water phase. On approach to the neat-water surface, that transition occurs once just above 10\angs from the surface, and again at 5\angs from the surface and below. The onset of orientation at 10\angs appears to be an artifact of the small data set and the normalization scheme, as the isotropic behavior resumes between 5-10\angs. Below 5\angs, however, the orientation persists and the \suldiox~begins to interact with the topmost surface waters, and orients accordingly. In the saturated system, the same trend occurs, however the onset of the perpendicular orientation begins at approx. 8\angs above the water surface. The layer of adsorbed \suldiox~already present in the saturated system most likely interacts with the transiting \suldiox~molecule. Also, topmost water molecules from the surface move up to a few\angs within the \suldiox~layer and interact with the transiting \suldiox~further from the surface than those in the neat-water system.

  % talk about phi differences
  With a mostly perpendicular bisector angle, it is expected that the values of $\phi$ would be isotropic relative to the reference axis. This is the case in both systems with one exception in the neat-water system. At the water surface and just below from 0\angs to 5\angs in the water phase, the $\theta$ profile broadens, and a clear trend appears in the profile of $\phi$. This corresponds to a \suldiox~orienting more flat to the surface (inclined up to 60 degrees from the surface normal). However, below this 5\angs region, the \suldiox~resumes an isotropic orientation as it becomes fully solvated by bulk waters.

  %Upon approaching the saturated surface at approx. 5\angs, the \suldiox~$\phi$ orientation distribution begins to cluster near $\cos(\phi)=1$, with the $\theta$ distribution remaining more isotropic, but with a trend of $\cos(\theta)>0$. At 5\angs the \suldiox~begins interacting with the other \suldiox~molecules that sit atop the water, and the resulting orientation distribution suggests that contact with the \suldiox~layer causes the adsorbing molecule to lie more flat to the surface. Within this same region from 0-5\angs above the surface, the $\phi$ distribution of the neat-\wat~system remains isotropic. The intensity of the distribution (darker blue) also indicates that the \suldiox~spends little time in this region, as it is quickly adsorbed further into the water bulk.
